\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{setspace}

\begin{document}

\begin{center}
    \textbf{\Large Department of Computer Engineering}\\
    University of Peradeniya\\[0.3cm]
    \textbf{CO2060 – Software Systems Design Project}\\[0.3cm]
    Date: January 8, 2026\\
    \textbf{Team: Invictus}\\
\end{center}

\vspace{0.5cm}

\section*{CO2060 Software System Design Project Timeline}

\subsection*{Phase 1: Planning (Jan 08 – Jan 15)}
\begin{itemize}
    \item Finalize project scope and objectives.
    \item Discuss system Framework:
    \begin{itemize}
        \item  Frontend Framework
        \item  Discuss Backend Tools
        \item  ML model training
    \end{itemize}
    \item Set up development environment and tools.
\end{itemize}

\subsection*{Phase 2: Frontend Prototype (Jan 18 – Jan 31)}
\begin{itemize}
    \item Implement frontend frames with React, TS + Vite.
    \item Discussing Front end user registration \& dashboard.
    \item Implement the Dashboard page.
    \item Implement a user and company registration UI page.
\end{itemize}

\subsection*{Phase 3: ML model train (Feb 1 – Feb 20)}
\begin{itemize}
    \item Connect with the Kaggle host and dataset, taking MIMI.
    \item Coding with Google Colab b.
\end{itemize}

\subsection*{Phase 4: Merge model to frontend (Feb 25 – Mar 1)}
\begin{itemize}
    \item Testing audio file uploading audio.
    \item Fixing UI parts and discuss sessions.
\end{itemize}

\subsection*{Phase 5: Testing \& backend devops (Mar 2 – Mar 16)}
\begin{itemize}
    \item Testing model and finalizing model setup.
    \item Users and company communication launch.
\end{itemize}

\subsection*{Phase 6: Documentation \& MVP (Mar 17 – Mar 31)}
\begin{itemize}
    \item Prepare user and developer documentation.
    \item Finalize report and submit working MVP.
\end{itemize}

\section*{Next Semester Upgrades (After-Mar 31)}
\begin{itemize}
    \item Develop service station and Google Maps into site.
    \item Enhanced documentation.
    \item Add advanced automation feature.
    \item Improve chatbot UI/UX.
    \item Strating develop mobile application.
\end{itemize}

\section*{Weekly Schedule Overview}

\begin{longtable}{|c|c|p{8cm}|}
\hline
\textbf{Week} & \textbf{Duration} & \textbf{Key Activities} \\
\hline
Week 1 & Jan 8 – Jan 15 & Project planning, framework definition, model identification, tool selection \\
\hline
Week 2 & Jan 18 – Jan 31 & React, Ts + Vite setup, UI assets \\
\hline
Week 3 & Feb 01 - Feb 20 & Model training \\
\hline
Week 4 & Feb 25 – Mar 1 & First Testing model \\
\hline
Week 5 & Mar 2 – Mar 16 & Model finilize \\
\hline
Week 6 & Mar 17 – Mar 31 & documentation, MPV feedback from users \\
\hline
\end{longtable}

\end{document}
